---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# SRRMLR

<!-- badges: start -->
<!-- badges: end -->

The goal of SRRMLR is to provides an tractable algorithm for building a multinomial logistic regression model with the model proposed in [Wen et al. (2020)]. The proposed method combines the merits of rank reduction and variable selection, constructing a parameter matrix with row sparsity and low-rank. Four other baseline methods are also included for comparison (grouped/ungrouped multinomial lasso [Simon et al. (2013)]; NNET [Ripley et al. (2016)]; RRVGLM [Yee and Hastie (2003)]). As a representative example, the HAM10000 dataset is included as well. See Simultaneous Dimension Reduction and Variable Selection for Multinomial Logistic Regression' for further information of this algorithm and related backgrounds.

"Function.R" file includes the prerequisite functions which perform SRRMLR with specific sparsity, rank and start points.
"Simulation.R" file generates simulation data and do the simulation analysis.
"cv_srrmlr.R" chooses the best sparsity and rank for our target dataset X and Y, providing the logistic model and corresponding prediction error. Meanwhile, the results of other 4 methods are listed in output.
"cmp.R" performs an averaged result for "cv_srrmlr.R" and presents the summary of results as output.

## Installation

You can install the released version of SRRMLR from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SRRMLR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SRRMLR)
## basic example code

fit = cv_srrmlr(HAM$hamimgs, HAM$hamlab)
fit$tab
```
